---
title: "Practical 1"
---
***PLEASE NOTE: On many occasions, I have only shown the first 5 rows of tables generated inorder to ensure the readability of the webpage as a whole.***

```{r echo=FALSE, results='hide'}
library(knitr)  # For neat table formatting
```

## Question One
Find all rows in “airquality” that have missing values.

```{r}
data_airquality <- airquality
missing_rows <- data_airquality[!complete.cases(data_airquality), ]
```
```{r}
#| echo: false
kable(missing_rows, caption = "Rows with Missing Values")
```

## Question Two
Find mean, sd, min, max for each of temperature and ozone level.

### Finding statistical information on 'Temp' data
```{r}
temp_stats <- data.frame(
  Statistic = c("Mean", "Standard Deviation", "Min", "Max"),
  Value = c(
    mean(data_airquality[["Temp"]], na.rm = TRUE),
    sd(data_airquality[["Temp"]], na.rm = TRUE),
    min(data_airquality[["Temp"]], na.rm = TRUE),
    max(data_airquality[["Temp"]], na.rm = TRUE)
  )
)
```
```{r}
#| echo: false
kable(temp_stats, col.names = c("Statistic", "Value"))
```

### Finding statistical information on 'Ozone' data
```{r}
ozone_stats <- data.frame(
  Statistic = c("Mean", "Standard Deviation", "Min", "Max"),
  Value = c(
    mean(data_airquality[["Ozone"]], na.rm = TRUE),
    sd(data_airquality[["Ozone"]], na.rm = TRUE),
    min(data_airquality[["Ozone"]], na.rm = TRUE),
    max(data_airquality[["Ozone"]], na.rm = TRUE)
  )
)
```
```{r}
#| echo: false
kable(ozone_stats, col.names = c("Statistic", "Value"))
```

## Question Three
Fit a simple linear regression model to these data, i.e. find the 'Beta' estimates, using the equation above (mentioned in the prac breakdown), and matrix calculations in R.
```{r}
data_cars <- cars

Y <- data_cars[["dist"]]
X <- cbind(1, cars[["speed"]])

beta_hat <- solve( t(X) %*% X ) %*% t(X) %*% Y
```
```{r echo=FALSE}
result <- data.frame(t(beta_hat))
colnames(result) <- c("(Intercept)", "Speed")
print(result, row.names = FALSE)
```

## Question Four
Checking that the same estimates are found as when fitting the linear regression model using lm() in R.
```{r}
model_test <- lm(dist ~ speed, data = cars)
```
```{r echo=FALSE}
coef(model_test)
```



