---
title: "Practical 1"
format: html
---

# Question One
Find all rows in “airquality” that have missing values. Note that the airquality dataset in R is always available (just type airquality in the console to see it).

```{r}
data_airquality <- airquality
```

## Find the rows with missing values
```{r}
missing_rows <- data_airquality[!complete.cases(data_airquality), ]
```
The rows with missing values are shown below:
```{r}
#| echo: false
print(missing_rows)
```

# Question 2
Find mean, sd, min, max for each of temperature and ozone level.

```{r}
library(knitr)  # For neat table formatting
data_airquality <- airquality
```

## Finding statistical information on 'Temp' data
```{r}
temp_stats <- data.frame(
  Statistic = c("Mean", "Standard Deviation", "Min", "Max"),
  Value = c(
    mean(data_airquality[["Temp"]], na.rm = TRUE),
    sd(data_airquality[["Temp"]], na.rm = TRUE),
    min(data_airquality[["Temp"]], na.rm = TRUE),
    max(data_airquality[["Temp"]], na.rm = TRUE)
  )
)
```

```{r}
#| echo: false
kable(temp_stats, col.names = c("Statistic", "Value"))
```

## Finding statistical information on 'Ozone' data
```{r}
ozone_stats <- data.frame(
  Statistic = c("Mean", "Standard Deviation", "Min", "Max"),
  Value = c(
    mean(data_airquality[["Ozone"]], na.rm = TRUE),
    sd(data_airquality[["Ozone"]], na.rm = TRUE),
    min(data_airquality[["Ozone"]], na.rm = TRUE),
    max(data_airquality[["Ozone"]], na.rm = TRUE)
  )
)
```

```{r}
#| echo: false
kable(ozone_stats, col.names = c("Statistic", "Value"))
```

# Question 3

For linear regression, parameter estimates can be found as follows: 
Here, Y is the response variable, and X is the design matrix. The cars data (an R data set, also always available in R) contains two variables: speed and distance to stop. Fit a simple linear regression model to these data, i.e. find the  estimates, using the equation above, and matrix calcuations in R.

```{r}
data_cars <- cars

Y <- data_cars[["dist"]]
X <- cbind(1, cars[["speed"]])

beta_hat <- solve(t(X)%*%X) %*% t(X)%*%Y
print(beta_hat)
```

# Question 4
Check that you get the same  estimates as when fitting the linear regression model using lm() in R.

```{r}
model_test <- lm(dist ~ speed, data = cars)
print(coef(model_test))
```



